\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[tmargin=1cm, bmargin=1cm, lmargin=2cm, rmargin=2cm]{geometry}
\usepackage{array}
\usepackage{enumitem}

% Font Arial
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Predefined colors
\usepackage{xcolor}
\definecolor{bgleftcol}{HTML}{7D5A9C}      % Lavanda morado
\definecolor{headercolor}{HTML}{7D5A9C}
\definecolor{iconcolor}{HTML}{7D5A9C}
\definecolor{iconcolor}{HTML}{7D5A9C}
\definecolor{lightbg}{HTML}{f8f9fa}

% URL
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=headercolor,
    urlcolor=headercolor,
    citecolor=headercolor
}

% Do not indent paragraphs
\setlength{\parindent}{0pt}

% Section and subsection styles
\usepackage{titlesec}
\titleformat{\section}%
    {\normalfont\huge\bfseries\color{headercolor}}%
    {\thesection}{1em}{}%
    [\color{headercolor}{\titlerule[0.8pt]}\vspace{0.3cm}]

\titleformat{\subsection}%
    {\normalfont\Large\bfseries\color{headercolor}}%
    {\thesubsection}{1em}{}%
    [\color{headercolor}{\titlerule[0.5pt]}\vspace{0.2cm}]

\titleformat{\subsubsection}%
    {\normalfont\large\bfseries\color{headercolor}}%
    {\thesubsubsection}{1em}{}%

% Job entry
\newcommand{\jobentry}[3]{
    {\Large\bfseries #1}
    %
    \hfill
    %
    #2
    %
    \vspace{0.2cm} \\
}

\newcommand{\projectentry}[2]{
    {\large\bfseries #1 \hfill #2} \\ \vspace{-0.5cm}
}

% Skill entry for inline skills
\newcommand{\skillentry}[2]{
    {\large\color{iconcolor}#1} #2 \quad
}

% Contact info command
\newcommand{\contactinfo}[2]{
    {\large\color{iconcolor}#1} #2 \quad
}

% Icons
\usepackage[fixed]{fontawesome5}

% Sensitive information
\input{private/private-information.tex}
\def\myname{Mileivi Zharick Esperanza Lombana Bohórquez}

\pagestyle{empty}
\begin{document}

% Header section
\begin{center}
    {\Huge\bfseries\color{headercolor}\myname}

    \vspace{0.3cm}

    {\Large Junior Software Engineer}

    \vspace{0.5cm}

    % Contact information in a single line
    \contactinfo{\faPhone}{\myphone}
    \contactinfo{\faAt}{\myemail}
    \contactinfo{\faGithub}{\href{https://github.com/Mileiviii18}{Mileiviii18}}
    {\large\color{iconcolor}\faHome} \myhome
\end{center}

% Professional summary
\colorbox{lightbg}{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{
\vspace{0.3cm}
    Junior QA Engineer with hands-on experience in automated testing and software 
    quality assurance across different environments: frontend, backend, APIs, and mobile 
    applications.
    Holds a degree in Software Analysis and Development, with a solid technical 
    background and experience using Selenium and Python for test automation, as well as 
    manual API testing with tools like Insomnia.
    Has contributed to projects involving validations for web interfaces, service endpoints, 
    and mobile apps, applying testing methodologies to ensure stable functionality and a 
    strong user experience.
    Known for a proactive attitude, strong organizational skills, and teamwork, with a 
    clear goal to keep growing as a QA Automation Engineer and bring value to agile and 
    collaborative development environments.
\vspace{0.3cm}
}}

\section*{Recent Experience}

\jobentry{Junior QA Engineer at Microsoft}{Jan 2025 -- July 2025}

\begin{tabular}{l m{15.7cm}}
    {\large\color{iconcolor}\faBug} & Performed comprehensive testing of frontend 
    and backend components to ensure alignment with product requirements and wireframes. \\[0.5cm]

    {\large\color{iconcolor}\faEye} & Reviewed UI/UX elements for consistency, 
    usability, and compliance with design specifications, identifying and 
    reporting visual and functional issues. \\[0.5cm]

    {\large\color{iconcolor}\faTasks} & Validated user stories (US) to ensure 
    completeness and functional accuracy before release, working closely with 
    developers and designers in agile environments. \\[0.5cm]

    {\large\color{iconcolor}\faCheckCircle} & Contributed to the delivery of 
    high-quality software by executing manual tests, documenting results, and 
    verifying fixes across various platforms.
\end{tabular}

\vspace{0.5cm}

\begin{flushright}
%
    \small Full work history available at
    \href{https://www.linkedin.com/in/mile1817/}{\faLinkedin Mileivi-QA}
    %
    \end{flushright}

%\vfill
\subsection*{Key Projects}

\projectentry{Juna – Chat Violence Detection Web App}{Microsoft (Social Project)}

\begin{itemize}
    \item Collaborated on a web application that detects types of violence 
    in WhatsApp chats using AI. The system processed uploaded chat `.txt` files, 
    cleaned and preprocessed data in the backend, and returned predictions based on trained AI models.
    
    \item Executed functional and non-functional testing across the entire system — including 
    frontend, backend; API endpoints — validating data flow, UI behavior, and system responses.

    \item Wrote and executed automated tests using \texttt{Selenium} and \texttt{Python}, 
    simulating user interactions in Microsoft Edge to validate front-end behavior. Also created 
    scripts to verify UI content and consistency.

    \item Performed manual API testing with \texttt{Insomnia}, validating backend responses 
    (201, 400, 500) for multiple file types and endpoint scenarios both locally and in deployment.

    \item Documented manual test cases in GitHub, detailing steps, expected outcomes, actual results, 
    and including screenshots for failure analysis based on user stories and acceptance criteria.

    \item Supported unit test debugging in the frontend, contributing to bug 
    identification that affected component behavior and integration.

    \item Participated in Scrum sprints, reviewing user stories, occasionally leading daily meetings, 
    and helping coordinate development and QA priorities within the team.

\end{itemize}

\section*{Technical Skills}
%
\begin{tabular}{l m{12cm}}
%
{\large\color{iconcolor}\faPython} \textbf{Python} & Data processing, automation 
scripting, and UI test automation using Selenium \\[0.4cm]
%
{\large\color{iconcolor}\faBug} \textbf{Testing} & Functional and non-functional 
testing. Manual API testing with Insomnia. Automated UI tests with Selenium \\[0.4cm]
%
{\large\color{iconcolor}\faLaptopCode} \textbf{QA \& Automation} & Test case documentation, 
user story validation, debugging unit tests, and verifying UI consistency \\[0.4cm]
%
{\large\color{iconcolor}\faUsers} \textbf{Agile Methodologies} & Scrum participation: 
sprint reviews, daily meetings, and team coordination in absence of PM/PO \\[0.4cm]
%
{\large\color{iconcolor}\faGithub} \textbf{Version Control} & Test documentation and 
collaboration using GitHub
%
\end{tabular}

\section*{Education}

\textbf{Software Analysis and Development} \hfill SENA \hfill 2023–2025

\end{document}